Supplemental Materials for the paper: \\Pesticides pollution of small streams in Germany

### 2016-07-18 supplement/Supplemental_Materials.tex
include tabular data overview

\documentclass[pdftex,a4paper]{scrreprt}
\usepackage[utf8]{inputenc}       
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage[
	round,	%(defaultage in the main file and \input ) for round parentheses;
	authoryear,% (default) for author-year citations;
	sort,		% orders multiple citations into the sequence in which they 
]{natbib}	
\usepackage{csvsimple}  % read csv files into Latex

@@

\begin{table}[htbp]
\caption{Overview on chemical samples. Only data from running waters and grab sampling is shown.}
\begin{tabular}{lllrrr}
state\textsuperscript{a} & begin & end & no. sites & no. samples & no. compounds\textsuperscript{b} \\
BW & 2005-01-03 & 2014-10-02 & 118 & 4569 & 127 \\ 
BY & 2006-04-19 & 2013-12-18 & 19 & 297 & 157 \\ 
HE & 2007-01-15 & 2014-12-18 & 68 & 2512 & 144 \\ 
MV & 2005-03-08 & 2014-12-17 & 135 & 1535 & 227 \\ 
NI & 2014-03-24 & 2014-10-13 & 3 & 17 & 226 \\ 
NW & 2005-01-11 & 2015-01-22 & 1320 & 10985 & 204 \\ 
RP & 2005-01-05 & 2013-12-18 & 44 & 1277 & 278 \\ 
SH & 2005-04-26 & 2014-11-26 & 273 & 1419 & 180 \\ 
SL & 2005-01-03 & 2013-12-09 & 6 & 420 & 57 \\ 
SN & 2005-01-02 & 2013-12-18 & 917 & 17052 & 173 \\ 
ST & 2005-01-10 & 2015-03-25 & 46 & 712 & 93 \\ 
TH & 2005-01-31 & 2014-12-10 & 100 & 1441 & 76 \\ \hline
\textbf{Total} & 2005-01-02 & 2015-03-25 & 3049 & 42236 & 484 \\  \hline
\end{tabular}
\\[1em]
\textsuperscript{a}: Abbreviation according to ISO 3166-2:DE .\\
\textsuperscript{b}: Including metabolites.
\label{tab:phch}
\end{table}

>>>>

\documentclass[pdftex,a4paper]{scrreprt}
\usepackage[utf8]{inputenc}       
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{booktabs}

\usepackage[
	round,	%(defaultage in the main file and \input ) for round parentheses;
	authoryear,% (default) for author-year citations;
	sort,		% orders multiple citations into the sequence in which they 
]{natbib}	
\usepackage{csvsimple}  % read csv files into Latex

@@

% table generate in do_overview.R
\input{phchoverview}
